A Mechanised Library for Generic (Co)Programming

### 2024-01-31 paper/paper.tex
Some structure, plus some Coq code

>>>>

\section{Mechanising Extractable Containers}

\dcas{Subsections are tentative topics to remember what I need to fill in here,
but these are not final}

Our goals are: (1) that the mechanisation of hylomorphisms and their laws are
axiom-free; and (2) Coq hylomorphisms can be extracted to recursive OCaml
functions that use no instances of \mintinline{OCaml}{Obj.magic}. Note that
although the use of \mintinline{OCaml}{Obj.magic} is safe in the code extracted
by Coq, its presence may prevent some optimisations by the OCaml
compiler\footnote{\dcas{I read this somewhere, search \& add reference/link}}.

\subsection{Functors and Containers}

\dcas{A first approach (problems with extraction, lots of Obj.magic, etc)}
\begin{minted}{Coq}
  Record Container (Shape : Set) (Pos : Shape -> Set) (X : Set) :=
    { shape : Shape; contents : Pos shape -> X }.
\end{minted}

\subsection{A Type for Morphisms}

\section{Extracting Certified Hylomorphisms}

\dcas{TODO: Hylo mechanisation, Hylo laws}

\subsection{Algebras}

\subsection{(Recursive) Coalgebras}

\section{Examples}

\paragraph{Quicksort \& Mergesort}

\dcas{What else?}
